Preregistration: Changes

### 2023-07-11 preregistration_changes.Rmd
Major updates Implemented feedback

@@

This includes (a) text-based media news consumption, (b) video-based media news consumption, (c) residency is Vienna, (d) self-reported physical health, (e) living space (in squaremeter), (f) access to balcony, (g) access to garden, (h) employment status, (i) disposition to take risks, and (j) locus of control.

The following variables I originally planned to include as control variables. However, their inclusion led to the deletion of too many cases/observations. I hence decided against their inclusion. This includes (a) household size, (b) work hours per week, (c) home office, (d) household income.

@@

Reviewer feedback required changes regarding the imputation strategy

- Before: predictive mean matching with n = 1 data-sets; now: multiple imputation (also predictive mean matching) with n = 5 data-sets.
- Before: remove participants with > 50% missing data; now: include all participants
- Before: remove variables leading to much attrition; now: include all variables

>>>>

## Wording Hypotheses

Before: Hypothesis: The within-person effects of all types of COVID-19 related social media use on all types of well-being indicators---while controlling for several stable and varying covariates such as sociodemographic variables and psychological dispositions---will be trivial.

Now: "Hypothesis: The within-person effects of all measures of COVID-19 related social media use (types: reading, liking and sharing, posting; channels: Twitter, Instagram, Facebook, YouTube, WhatsApp) on all measures of well-being indicators (positive affect, negative affect, life satisfaction)---while controlling for several stable and varying covariates such as sociodemographic variables and psychological dispositions (see below)---will be trivial.

Explanation: The wording of the hypotheses was changed slightly. Instead of "trivial", it not states "very small". The reason was that trivial contains a normative element (irrelevant). Instead, I now state "very small", which seems more objective. Some might consider very small effects trivial, others not.

In addition, I link to the control variables explicated below.

@@

This includes residency is Vienna, self-reported physical health, living space (in squaremeter), access to balcony, access to garden, and employment status.

I additionally planned to control for satisfaction with democracy and other types of media use. However, it's likely that they also serve as mediators, which is why I will not include them in the main models. They will, however, be reported in the supplementary analyses.

@@

After having received feedback from colleagues who are experts on missing data analyses, I changed the imputation strategy.

- Before: predictive mean matching with n = 1 data-sets; now: multiple imputation (also predictive mean matching) with n = 5 data-sets.
- Before: remove participants with > 50% missing data; now: include all participants
